### 2022-12-02 definitions.tex
up
details

\begin{proof}
Let $J=\downarrow Reach(S)$. Now resilience remains to the following property: $\forall s \in S,  \exists s'' \in I, ~ s' \rightarrow^{*} s''$. This property is a liveness property that would allow to decide LTL but LTL has been proved undecidable for Lossy Channel Systems (LCS) for which Reach=$\downarrow Reach$.
Since LCS are effective WSTS with strong monotony (with an adequate semantics), we conclude.
\end{proof}

>>>>

\begin{proof}
Let $J=\downarrow Reach(S)$ and $I = \uparrow t$ where $t \in S$. Now resilience remains to the following property: $\forall s \in S,  \exists s'' \in I, ~ s' \rightarrow^{*} s''$. Let us translate this property for LCS for which Reach=$\downarrow Reach$: $I = \uparrow (q,\epsilon) = (q, \Sigma^*)$. This property can be used to express the liveness property that there is an infinite run passing infinitely often through control-state $q$; this LTL-property has been proved undecidable for Lossy Channel Systems (LCS) \cite{DBLP:conf/icalp/AbdullaJ94}.
Since LCS are effective WSTS with strong monotony (with an adequate semantics), we conclude.
\end{proof}
